---
title: "GY7702 CW1"
author: "Jacob Embery"
date: "05/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
```

```{r load_libraries, warning=FALSE, message=FALSE}
library(tidyverse)
```

#Question 1:


##Create the vector of 25 numbers between 1 and 7 listed below, using the function c. Assume those values
##represent the answers to a survey question, following the scale presented further below.

## [1] NA 3 4 4 5 2 4 NA 6 3 5 4 0 5 7 5 NA 5 2 4 NA 3 3 5 NA

## 1 = completely disagree
## 2 = disagree
## 3 = somehow disagree
## 4 = neither agree nor disagree
## 5 = somehow agree
## 6 = agree
## 7 = completely agree
## NA = missing value


##**Question 1.1:** write the code necessary to check whether all participants to the survey either completely
## disagree or completely agree, once the missing values are excluded.

```{r}
#Before doing anything you must remove NA values from the vector
survey_answer = survey_answer[
  !is.na(survey_answer)]

#1 = completely disagree so this asks the vector if all values are equal to 1.
print(paste(
  "Do all participants completely disagree?", all(survey_answer == 1)
  ))

#7 = completely agree, same as above.
print(paste(
  "Do all participants completely agree?", all(survey_answer == 7)
  ))
```



##**Question 1.2:** write the code necessary to extract the indexes related to the participants in the survey who
##at least somehow agree or more.

```{r}
#the which function used to extract 5, 6 and 7 (in the vector c) out of the survey_answer vetor
which(survey_answer %in% c(5,6,7))
```



#Question 2:


##**Question 2.1:** Install the library palmerpenguins.
  
```{r load_libraries, warning=FALSE, message=FALSE}
library(palmerpenguins)
library(dplyr)
library(tidyverse)

pengtable <- palmerpenguins::penguins
```



##**Question 2.2:** write the code necessary to create a table showing species, island, bill length and body mass
##of the 10 Gentoo penguins in the penguins table with the highest body mass.
  
```{r}
pengtable %>%
  dplyr::select(species, island, bill_length_mm, body_mass_g) %>%
  dplyr::filter(species == "Gentoo") %>%
  dplyr::slice_max(body_mass_g, n = 10)
```



##**Question 2.3:** write the code necessary to create a table showing the average bill length per island, ordered
##by average bill length.
  
```{r}
 pengtable %>%
  dplyr::select(bill_length_mm, island) %>% 
  dplyr::group_by(island) %>%
  dplyr::mutate(
    avg_bill_length_mm = mean(bill_length_mm)
  ) %>%
  dplyr::arrange(avg_bill_length_mm)
```



##**Question 2.4:** write the code necessary to create a table showing the minimum, median and maximum
##proportion between bill length and bill depth by species.
  
```{r}
pengtable %>%
    na.omit(pengtable) %>%
    dplyr::select(bill_length_mm, bill_depth_mm, species) %>%
    dplyr::mutate(
      min_proportion = min(bill_length_mm) / min(bill_depth_mm)
    ) %>%
    dplyr::mutate(
      med_proportion = median(bill_length_mm) / median(bill_depth_mm)
    ) %>%
    dplyr::mutate(
      max_proportion = max(bill_length_mm) / max(bill_depth_mm)
    ) %>%
    dplyr::group_by(species)
```




















```{r include=FALSE}
rm(list = ls())
```

